Relating games of Menger, countable fan tightness, and selective separability

### 2018-03-02 articles/relating-games-menger-cft-ss/article.tex
add keywords, subject classes
incorporate referee typesetting feedback

% \keywords{TODO}
% \subjclass[2010]{}

@@

The similar notations for \(\omega\)-covers \(\Omega_X\) and
blades \(\Omega_{X,x}\) is well-established, see e.g.
\cite[Topological games and Ramsey theory]{19362020070101} (wherein
the notation is more succently given as \(\Omega,\Omega_x\)).  The
relationship between such sets becomes apparent in the study of
\(C_p\)-theory; for this reason we choose to always denote the space
explicitly to help distinguish the ambient spaces when discussing
the relationship between \(\Omega_X\) and
\(\Omega_{C_p(X),\vec 0}\).

@@

Of course, one may easily observe that a selective separable space is
separable, and \(SS\Rightarrow CDFT\).
In \cite{MR2678950} Barman and Dow demonstrated that all
separable Frechet spaces are selectively separable. They were also able
to produce a space which is selectively separable, but does not allow
\(\plII\) a winning strategy in the selective separability game.

@@

\begin{notation}
  If \(\schSelProp{\mc A}{\mc B}\) characterizes the property \(P\),
  then we say \(\plII\win\schSelGame{\mc A}{\mc B}\) characterizes
  \(P^+\) (``strategically \(P\)''), and
  \(\plII\markwin\schSelGame{\mc A}{\mc B}\) characterizes
  \(P^{+mark}\) (``Markov \(P\)'').
  Of course, \(P^{+mark}\Rightarrow P^+ \Rightarrow P\).
\end{notation}

@@

\begin{question}\label{mainQuestion}
  Does \(SS^+\) imply \(SS^{+mark}\)?
\end{question}

The solution is already known to be ``yes'' in the context of countable spaces
\cite{MR2678950}. However in general, winning strategies in selection games
cannot be improved to be winning Markov strategies. In
\cite{clontzMengerCMUC} the author showed that \(M^+\) implies
\(M^{+mark}\) for second-countable spaces; however, the one-point
Lindel\"of-ication \(\onePtLind{\omega_1}\) of a discrete space of size
\(\omega_1\) is a simple
example of a regular non-second-countable space which is
\(M^+\) but not \(M^{+mark}\) (equivalently, not \(\sigma\)-compact).
It will later be shown that it is no coincidence
that countable \(SS^+\) implies \(SS^{+mark}\) and
second-countable \(M^+\) implies \(M^{+mark}\).

@@

\begin{theorem}[Lem 2.7 of \cite{MR2678950}]
  The following are equivalent for any topological space \(X\).
  \begin{itemize}
    \item \(X\) is \(SS\).
    \item \(X\) is separable and \(CDFT\).
    \item \(X\) has a countable dense subset \(D\) where
          \(CDFT_x\) holds for all \(x\in D\).
  \end{itemize}
\end{theorem}

\begin{theorem}
  The following are equivalent for any topological space \(X\).
  \begin{itemize}
    \item \(X\) is \(SS\) (resp. \(SS^+\), \(SS^{+mark}\)).
    \item \(X\) is separable and \(CDFT\)
          (resp. \(CDFT^+\), \(CDFT^{+mark}\)).
    \item \(X\) has a countable dense subset \(D\) where
          \(CDFT_x\) (resp. \(CDFT_x^+\), \(CDFT_x^{+mark}\))
          holds for all \(x\in D\).
  \end{itemize}
\end{theorem}

@@

  Now let \(\sigma_i\) be a witness for \(CDFT_{d_i}^{+mark}\)
  for each \(i<\omega\). We define the Markov strategy \(\tau\) for the
  \(SS\) game by
  \[
    \tau(D,n)
      =
    \bigcup_{i\leq n}
    \sigma_i(D,n-i)
  .\]

  Let \(\<D_0,D_1,\dots\>\in\mc D_X^\omega\).
  By \(CDFT_{d_i}^{+mark}\), we have
  \[
    d_i
      \in
    \cl{\bigcup_{i\leq n<\omega}\sigma_i(D_n,n-i)}
      \subseteq
    \cl{\bigcup_{i\leq n<\omega}\tau(D_n,n)}
      \subseteq
    \cl{\bigcup_{n<\omega}\tau(D_n,n)}
  \]
  and as \(D\subseteq\cl{\bigcup_{n<\omega}\tau(D_n,n)}\)
  it follows that
  \[
    X
      \subseteq
    \cl D
      \subseteq
    \cl{\cl{\bigcup_{n<\omega}\tau(D,n)}}
      =
    \cl{\bigcup_{n<\omega}\tau(D,n)}
  .\]
  Therefore \(\tau\) witnesses \(SS^{+mark}\).
\end{proof}

So amongst separable spaces, we see that \(SS\)
(resp. \(SS^+\), \(SS^{+mark}\)) and
\(CDFT\) (resp. \(CDFT^+\), \(CDFT^{+mark}\))
are equivalent. We now further bridge the gap between \(CDFT\)
and \(CFT\) in the context of function spaces.
Consider the following result of Arhangel'skii.

@@

This result may similarly be generalized in a game theoretic sense.
In addition, this proof will demonstrate the equivalence of
\(CFT\) and \(CDFT\) in \(C_p(X)\).
It is unknown to the author whether Arhangel'skii
used a strategy similar to the following proof in \cite{MR837289},
but Sakai employed a similar technique
in \cite{MR964873} to relate the \(\Omega\)-Rothberger and
countable strong fan tightness properties
(and essentially, the countable strong dense fan tightness property).
Due to the difficulty in obtaining an English translation of
\cite{MR837289}, we reprove Arhangel'skii's theorem above in our
more general context below.

\begin{proposition}
  Any witness for \(\Omega M\) (resp.
  \(\Omega M^+,\Omega M^{+mark}\))
  may be improved such that any final sequence of the chosen
  finite subcollections is an \(\omega\)-cover.
\end{proposition}

@@

  For \(\Omega M^+\), the winning strategy \(\sigma\) may be improved to
  \(\tau\) where
  \(
    \tau(\<\mc U_0,\dots,\mc U_n\>)
      =
    \bigcup_{i\leq n}\sigma(\<\mc U_i,\dots,\mc U_n\>)
  \). For \(\Omega M^{+mark}\), the winning Markov strategy \(\sigma\) may
  be improved to \(\tau\) where
  \(
    \tau(\mc U,n)
      =
    \bigcup_{i\leq n}\sigma(\mc U,i)
  \). Both improved strategies are easily seen to satisfy the proposition.
\end{proof}

@@

\begin{lemma}\label{mengerFanLemma1}
  Let \(X\) be a \(T_{3\frac{1}{2}}\) topological space.
  If \(X\) is \(\Omega M\)
  (resp. \(\Omega M^+\), \(\Omega M^{+mark}\)).
  then \(C_p(X)\) is \(CFT_{\vec 0}\)
  (resp. \(CFT_{\vec 0}^+\), \(CFT_{\vec 0}^{+mark}\)).
\end{lemma}

@@

  Assuming \(X\) is \(\Omega M^{+mark}\), choose a witness
  \(\sigma\) such that
  \[
    \bigcup_{i\leq n<\omega} \sigma(\mc U_n(B_n),n)
  \]
  is an \(\omega\)-cover of \(X\) for all \(i<\omega\).
  Now let
  \[
    \tau(B_n,n)
      =
    \left\{
      \vec x\in B_n
    :
      \vec x^{\leftarrow}\left[\left(-\frac{1}{2^n},\frac{1}{2^n}\right)\right]
        \in
      \sigma(\mc U_n(B_n),n)
    \right\}
  .\]
  We claim that \(\vec 0\in\cl{\bigcup_{n<\omega}\tau(B_n,n)}\).
  Let \(G\in[X]^{<\omega},\epsilon>0\). Choose \(i<\omega\) such that
  \(\frac{1}{2^i}<\epsilon\). Since
  \(\bigcup_{i\leq n<\omega} \sigma(\mc U_n(B_n),n)\) is an \(\omega\)-cover,
  we may choose \(i\leq n<\omega\) and
  \(\vec x^{\leftarrow}[(-\frac{1}{2^n},\frac{1}{2^n})]\in\sigma(\mc U_n(B_n),n)\)
  such that \(G\subseteq \vec x^{\leftarrow}[(-\frac{1}{2^n},\frac{1}{2^n})]\).
  Therefore \(G\subseteq \vec x^{\leftarrow}[(-\epsilon,\epsilon)]\).
  It follows that \(\vec x\in \tau(B_n,n)\cap[\vec 0,G,\epsilon]\), and thus
  every basic open neighborhood of \(\vec 0\) intersects
  \(\bigcup_{n<\omega}\tau(B_n,n)\).
\end{proof}

\begin{lemma}\label{mengerFanLemma2}
  Let \(X\) be a \(T_{3\frac{1}{2}}\) topological space.
  If \(C_p(X)\) is \(CDFT_{\vec 0}\)
  (resp. \(CDFT_{\vec 0}^+\), \(CDFT_{\vec 0}^{+mark}\)),
  then \(X\) is \(\Omega M\)
  (resp. \(\Omega M^+\), \(\Omega M^{+mark}\)).
\end{lemma}

@@

  Assuming \(C_p(X)\) is \(CDFT_{\vec 0}^{+mark}\), choose a witness
  \(\sigma\) such that
  \[
    \vec 0
      \in
    \cl{\bigcup_{n<\omega} \sigma(D(\mc U_n),n)}
  .\]
  Now let
  \[
    \tau(\mc U_n,n)
      =
    \{
      U_{\vec y,\mc U_n}
    :
      \vec y \in \sigma(D(\mc U_n),n)
    \}
      \in
    [\mc U_n]^{<\omega}S
  .\]
  We claim that \(\bigcup_{n<\omega}\tau(\mc U_n,n)\)
  is an \(\omega\)-cover.
  Let \(G\in[X]^{<\omega}\). The neighborhood \([\vec 0,G,\frac{1}{2}]\)
  contains some point \(\vec y\in \sigma(D(\mc U_n),n)\)
  for some \(n<\omega\). It follows
  that \(U_{\vec y,\mc U_n}\in\mc U_n\) and
  \(\vec y[X\setminus U_{\vec y,\mc U_n}]=\{1\}\). As a result
  \(G\cap(X\setminus U_{\vec y,\mc U_n})=\emptyset\), and therefore
  \(G\subseteq U_{\vec y,\mc U_n}\in\mc \tau(\mc U_n,n)\).
\end{proof}

\begin{theorem}\label{mengerFanTheorem}
  The following are equivalent for any \(T_{3\frac{1}{2}}\)
  topological space \(X\).
    \begin{itemize}
      \item \(X\) is \(\Omega M\)
            (resp. \(\Omega M^+\), \(\Omega M^{+mark}\)).
      \item \(C_p(X)\) is \(CFT\)
            (resp. \(CFT^+\), \(CFT^{+mark}\)).
      \item \(C_p(X)\) is \(CDFT\)
            (resp. \(CDFT^+\), \(CDFT^{+mark}\)).
    \end{itemize}
\end{theorem}

\begin{proof}
  Since \(\mc D_X\subseteq \Omega_{X,x}\), the second condition trivially
  implies the first. As \(C_p(X)\) is homogeneous, the \(C(D)FT\) properties
  follow from \(C(D)FT_{\vec 0}\). So the result follows from the
  previous lemmas.
\end{proof}

\section{A space which is \(CFT^+\) but not \(CDFT^{+mark}\)}

Our goal is to now demonstrate a space which is \(CFT^+\),
but not even \(CDFT^{+mark}\). To do so, we will find a space \(X\)
which is \(\Omega M^+\) but not \(\Omega M^{+mark}\), yielding \(C_p(X)\)
as our example.

@@

\begin{lemma}
  The following are equivalent for a regular topological space \(X\):
  \begin{itemize}
    \item \(X\) is \(\sigma\)-compact
    \item \(X\) is \(\Omega M^{+mark}\)
    \item \(X\) is \(M^{+mark}\)
  \end{itemize}
\end{lemma}

\begin{proof}
  The equivalence of \(\sigma\)-compact and \(M^{+mark}\) in regular spaces
  was shown in \cite{clontzMengerCMUC}. As \(\Omega M^{+mark}\)
  trivially implies \(M^{+mark}\), we need only demonstrate that
  if \(X=\bigcup_{n<\omega} K_n\) for \(K_n\) compact and increasing,
  then \(X\) is \(\Omega M^{+mark}\).

@@

\begin{theorem}\label{omega1OmegaMenger}
  Let \(\omega_1\) have the discrete topology. Then
  \(\onePtLind{\omega_1}\) is \(\Omega M^+\) but not \(\Omega M^{+mark}\).
\end{theorem}

\begin{proof}
  The proof that \(X=\onePtLind{\omega_1}\) is not
  \(\sigma\)-compact (and therefore not \(\Omega M^{+mark}\))
  follows from the fact that its countably infinite subsets
  are closed and discrete, so all of its compact subsets are finite.

@@

\begin{corollary}
  \(C_p(\onePtLind{\omega_1})\) is \(CFT^+\) but not \(CDFT^{+mark}\).
\end{corollary}

@@

\begin{question}
  Does there exist a separable subspace of \(C_p(\onePtLind{\omega_1})\)
  which is not \(CDFT^{+mark}\)?
\end{question}

@@

Barman and Dow
previously demonstrated that \(SS^+\) is equivalent to
\(SS^{+mark}\) amongst countable spaces.
A similar result by the author
showed that \(M^+\) is equivalent to \(M^{+mark}\) in second-countable
spaces. The following result generalizes both.

@@

  For \(t\in\omega^{<\omega}\), suppose
  \(Z_s\in\mc A\) has been defined for all \(s\leq t\). Note then that
  \(
    \{\sigma(\<Z_{t\rest1},Z_{t\rest2},\dots,Z_t,A\>:A\in\mc A\}
      \subseteq
    [\bigcup\mc A]^{<\omega}
  \)
  and therefore is countable.
  So choose \(Z_{t\concat\<n\>}\in\mc A\) for \(n<\omega\) such that
  \(
    \{\sigma(\<Z_{t\rest1},Z_{t\rest2},\dots,Z_t,A\>:A\in\mc A\}
      =
    \{\sigma(\<Z_{t\rest1},Z_{t\rest2},\dots,Z_t,Z_{t\concat\<n\>}\>):n<\omega\}
  \).

@@

  Define \(f\in\omega^\omega\) as follows.
  Let \(n<\omega\) and suppose that \(f\rest n\) has been already
  been defined. Then choose \(f(n)<\omega\) such that
  \(
    \sigma(\<Z_{f\rest1},Z_{f\rest2},\dots,Z_{f\rest n},A_{b^{\leftarrow}(f\rest n)}\>)
      =
    \sigma(\<Z_{f\rest1},Z_{f\rest2},\dots,Z_{f\rest n},Z_{f\rest (n+1)}\>)
  \).

@@

\begin{corollary}[\cite{MR2868880}]
  A countable space is \(SS^+\) if and only if it is
  \(SS^{+mark}\).
\end{corollary}

@@

\begin{corollary}
  A second-countable space is \(\Omega M^+\) if and only if
  it is \(\Omega M^{+mark}\).
\end{corollary}

@@

\begin{corollary}[\cite{clontzMengerCMUC}]
  A second-countable space is \(M^+\) if and only if
  it is \(M^{+mark}\).
\end{corollary}

\begin{proof}
  An easy adapatation of the preceding proof, replacing \(\omega\)-covers
  with open covers, and replacing \(F\in[X]^{<\omega}\) with \(x\in X\).
\end{proof}

\section{Strong variants of selection princples and games}

Let \(\schStrongSelProp{\mc A}{\mc B},\schStrongSelGame{\mc A}{\mc B}\)
be the natural variants of
\(\schSelProp{\mc A}{\mc B},\schSelGame{\mc A}{\mc B}\) where each choice
by \(\plII\) must either be a single element or singleton
(whichever is more convenient for the proof at hand), rather than a finite
set. Convention calls for denoting these as
\term{strong} versions of the corresponding selection princples and games,
although the ``strong Menger'' property is commonly known as ``Rothberger''
who first investigated the principle in \cite{Rothberger1938}. We will thus
call ``strong \(\Omega\)-Menger'' ``\(\Omega\)-Rothberger'' and shorten it
with \(\Omega R\), and otherwise attach the prefix ``s''
when abbreviating to all other strong variants.

\begin{theorem}
  The following are equivalent for any topological space \(X\).
  \begin{itemize}
    \item \(X\) is \(sSS\) (resp. \(sSS^+\), \(sSS^{+mark}\)).
    \item \(X\) is separable and \(sCDFT\)
          (resp. \(sCDFT^+\), \(sCDFT^{+mark}\)).
    \item \(X\) has a countable dense subset \(D\) where
          \(sCDFT_x\) (resp. \(sCDFT_x^+\), \(sCDFT_x^{+mark}\))
          holds for all \(x\in D\).
  \end{itemize}
\end{theorem}

@@

  Let \(\sigma_i\) be a witness for \(sCDFT_{d_i}^{+mark}\)
  for each \(i<\omega\).
  Again, we will partition each
  attack by \(\plI\) according to \(p\) into \(\omega\)-many subattacks, and
  defeat each subattack to produce a blade of \(d_n\).

@@

  Let \(\alpha\in\mc D_X^\omega\), and let \(\alpha_i\) be its subsequence
  removing all terms of index \(n\) such that \(p(n)\not=i\).
  By \(sCDFT_{d_i}^{+mark}\), we have
  \[
    d_i
      \in
    \cl{\{\sigma_i(\alpha_i(n),n):n<\omega\}}
      =
    \cl{\{\tau(\alpha(n),n):n\in p^{\leftarrow}(i)\}}
      \subseteq
    \cl{\{\tau(\alpha(n),n):n<\omega\}}
  \]
  and as \(D\subseteq\cl{\{\tau(\alpha(n),n):n<\omega\}}\)
  it follows that
  \[
    X
      \subseteq
    \cl D
      \subseteq
    \cl{\cl{\{\tau(\alpha(n),n):n<\omega\}}}
      =
    \cl{\{\tau(\alpha(n),n):n<\omega\}}
  .\]
  Therefore \(\tau\) witnesses \(SS^{+mark}\).
\end{proof}

>>>>

\keywords{Selection property, selection game,
limited information strategies, covering properties, Cp theory}

\subjclass[2010]{54C30, 54D20, 54D45, 91A44}

@@

The similar notations for \(\omega\)-covers \(\Omega_X\) and
blades \(\Omega_{X,x}\) is well-established, see e.g.
\cite[Topological games and Ramsey theory]{19362020070101} (wherein
the notation is more succinctly given as \(\Omega,\Omega_x\)).  The
relationship between such sets becomes apparent in the study of
\(C_p\)-theory; for this reason we choose to always denote the space
explicitly to help distinguish the ambient spaces when discussing
the relationship between \(\Omega_X\) and
\(\Omega_{C_p(X),\vec 0}\).

@@

Of course, one may easily observe that a selectively separable space is
separable, and \(SS\Rightarrow CDFT\).
In \cite{MR2678950} Barman and Dow demonstrated that all
separable Frechet spaces are selectively separable. They were also able
to produce a space which is selectively separable, but does not allow
\(\plII\) a winning strategy in the selective separability game.

@@

\begin{notation}
  If \(\schSelProp{\mc A}{\mc B}\) characterizes the property \(P\),
  then we say \(\plII\win\schSelGame{\mc A}{\mc B}\) characterizes
  \(P^+\) (``strategically \(P\)''), and
  \(\plII\markwin\schSelGame{\mc A}{\mc B}\) characterizes
  \(P^{\plusMark}\) (``Markov \(P\)'').
  Of course, \(P^{\plusMark}\Rightarrow P^+ \Rightarrow P\).
\end{notation}

@@

\begin{question}\label{mainQuestion}
  Does \(SS^+\) imply \(SS^{\plusMark}\)?
\end{question}

The solution is already known to be ``yes'' in the context of countable spaces
\cite{MR2678950}. However in general, winning strategies in selection games
cannot be improved to be winning Markov strategies. In
\cite{clontzMengerCMUC} the author showed that \(M^+\) implies
\(M^{\plusMark}\) for second-countable spaces; however, the one-point
Lindel\"of-ication \(\onePtLind{\omega_1}\) of a discrete space of size
\(\omega_1\) is a simple
example of a regular non-second-countable space which is
\(M^+\) but not \(M^{\plusMark}\) (equivalently, not \(\sigma\)-compact).
It will later be shown that it is no coincidence
that countable \(SS^+\) implies \(SS^{\plusMark}\) and
second-countable \(M^+\) implies \(M^{\plusMark}\).

@@

\begin{theorem}[Lemma 2.7 of \cite{MR2678950}]
  The following are equivalent for any topological space \(X\).
  \begin{itemize}
    \item \(X\) is \(SS\).
    \item \(X\) is separable and \(CDFT\).
    \item \(X\) has a countable dense subset \(D\) where
          \(CDFT_x\) holds for all \(x\in D\).
  \end{itemize}
\end{theorem}

\begin{theorem}
  The following are equivalent for any topological space \(X\).
  \begin{itemize}
    \item \(X\) is \(SS\) (resp. \(SS^+\), \(SS^{\plusMark}\)).
    \item \(X\) is separable and \(CDFT\)
          (resp. \(CDFT^+\), \(CDFT^{\plusMark}\)).
    \item \(X\) has a countable dense subset \(D\) where
          \(CDFT_x\) (resp. \(CDFT_x^+\), \(CDFT_x^{\plusMark}\))
          holds for all \(x\in D\).
  \end{itemize}
\end{theorem}

@@

  Now let \(\sigma_i\) be a witness for \(CDFT_{d_i}^{\plusMark}\)
  for each \(i<\omega\). We define the Markov strategy \(\tau\) for the
  \(SS\) game by
  \[
    \tau(D,n)
      =
    \bigcup_{i\leq n}
    \sigma_i(D,n-i)
  .\]

  Let \(\<D_0,D_1,\dots\>\in\mc D_X^\omega\).
  By \(CDFT_{d_i}^{\plusMark}\), we have
  \[
    d_i
      \in
    \cl{\bigcup_{i\leq n<\omega}\sigma_i(D_n,n-i)}
      \subseteq
    \cl{\bigcup_{i\leq n<\omega}\tau(D_n,n)}
      \subseteq
    \cl{\bigcup_{n<\omega}\tau(D_n,n)}
  \]
  and as \(D\subseteq\cl{\bigcup_{n<\omega}\tau(D_n,n)}\)
  it follows that
  \[
    X
      \subseteq
    \cl D
      \subseteq
    \cl{\cl{\bigcup_{n<\omega}\tau(D,n)}}
      =
    \cl{\bigcup_{n<\omega}\tau(D,n)}
  .\]
  Therefore \(\tau\) witnesses \(SS^{\plusMark}\).
\end{proof}

So amongst separable spaces, we see that \(SS\)
(resp. \(SS^+\), \(SS^{\plusMark}\)) and
\(CDFT\) (resp. \(CDFT^+\), \(CDFT^{\plusMark}\))
are equivalent. We now further bridge the gap between \(CDFT\)
and \(CFT\) in the context of function spaces.
Consider the following result of Arhangel'skii.

@@

This result may similarly be generalized in a game-theoretic sense.
In addition, this proof will demonstrate the equivalence of
\(CFT\) and \(CDFT\) in \(C_p(X)\).
It is unknown to the author whether Arhangel'skii
used a strategy similar to the following proof in \cite{MR837289},
but Sakai employed a similar technique
in \cite{MR964873} to relate the \(\Omega\)-Rothberger and
countable strong fan tightness properties
(and essentially, the countable strong dense fan tightness property).
Due to the difficulty in obtaining an English translation of
\cite{MR837289}, we reprove Arhangel'skii's theorem above in our
more general context below.

\begin{proposition}
  Any witness for \(\Omega M\) (resp.
  \(\Omega M^+,\Omega M^{\plusMark}\))
  may be improved so that any final sequence of the chosen
  finite subcollections is an \(\omega\)-cover.
\end{proposition}

@@

  For \(\Omega M^+\), the winning strategy \(\sigma\) may be improved to
  \(\tau\) where
  \(
    \tau(\<\mc U_0,\dots,\mc U_n\>)
      =
    \bigcup_{i\leq n}\sigma(\<\mc U_i,\dots,\mc U_n\>)
  \). For \(\Omega M^{\plusMark}\), the winning Markov strategy \(\sigma\) may
  be improved to \(\tau\) where
  \(
    \tau(\mc U,n)
      =
    \bigcup_{i\leq n}\sigma(\mc U,i)
  \). Both improved strategies are easily seen to satisfy the proposition.
\end{proof}

@@

\begin{lemma}\label{mengerFanLemma1}
  Let \(X\) be a \(T_{3\frac{1}{2}}\) topological space.
  If \(X\) is \(\Omega M\)
  (resp. \(\Omega M^+\), \(\Omega M^{\plusMark}\)).
  then \(C_p(X)\) is \(CFT_{\vec 0}\)
  (resp. \(CFT_{\vec 0}^+\), \(CFT_{\vec 0}^{\plusMark}\)).
\end{lemma}

@@

  Assuming \(X\) is \(\Omega M^{\plusMark}\), choose a witness
  \(\sigma\) such that
  \[
    \bigcup_{i\leq n<\omega} \sigma(\mc U_n(B_n),n)
  \]
  is an \(\omega\)-cover of \(X\) for all \(i<\omega\).
  Now let
  \[
    \tau(B_n,n)
      =
    \left\{
      \vec x\in B_n
    :
      \vec x^{\leftarrow}\left[\left(-\frac{1}{2^n},\frac{1}{2^n}\right)\right]
        \in
      \sigma(\mc U_n(B_n),n)
    \right\}
  .\]
  We claim that \(\vec 0\in\cl{\bigcup_{n<\omega}\tau(B_n,n)}\).
  Let \(G\in[X]^{<\omega},\epsilon>0\). Choose \(i<\omega\) such that
  \(\frac{1}{2^i}<\epsilon\). Since
  \(\bigcup_{i\leq n<\omega} \sigma(\mc U_n(B_n),n)\) is an \(\omega\)-cover,
  we may choose \(i\leq n<\omega\) and
  \(\vec x^{\leftarrow}[(-\frac{1}{2^n},\frac{1}{2^n})]\in\sigma(\mc U_n(B_n),n)\)
  such that \(G\subseteq \vec x^{\leftarrow}[(-\frac{1}{2^n},\frac{1}{2^n})]\).
  Therefore \(G\subseteq \vec x^{\leftarrow}[(-\epsilon,\epsilon)]\).
  It follows that \(\vec x\in \tau(B_n,n)\cap[\vec 0,G,\epsilon]\), and thus
  every basic open neighborhood of \(\vec 0\) intersects
  \(\bigcup_{n<\omega}\tau(B_n,n)\).
\end{proof}

\begin{lemma}\label{mengerFanLemma2}
  Let \(X\) be a \(T_{3\frac{1}{2}}\) topological space.
  If \(C_p(X)\) is \(CDFT_{\vec 0}\)
  (resp. \(CDFT_{\vec 0}^+\), \(CDFT_{\vec 0}^{\plusMark}\)),
  then \(X\) is \(\Omega M\)
  (resp. \(\Omega M^+\), \(\Omega M^{\plusMark}\)).
\end{lemma}

@@

  Assuming \(C_p(X)\) is \(CDFT_{\vec 0}^{\plusMark}\), choose a witness
  \(\sigma\) such that
  \[
    \vec 0
      \in
    \cl{\bigcup_{n<\omega} \sigma(D(\mc U_n),n)}
  .\]
  Now let
  \[
    \tau(\mc U_n,n)
      =
    \{
      U_{\vec y,\mc U_n}
    :
      \vec y \in \sigma(D(\mc U_n),n)
    \}
      \in
    [\mc U_n]^{<\omega}
  .\]
  We claim that \(\bigcup_{n<\omega}\tau(\mc U_n,n)\)
  is an \(\omega\)-cover.
  Let \(G\in[X]^{<\omega}\). The neighborhood \([\vec 0,G,\frac{1}{2}]\)
  contains some point \(\vec y\in \sigma(D(\mc U_n),n)\)
  for some \(n<\omega\). It follows
  that \(U_{\vec y,\mc U_n}\in\mc U_n\) and
  \(\vec y[X\setminus U_{\vec y,\mc U_n}]=\{1\}\). As a result
  \(G\cap(X\setminus U_{\vec y,\mc U_n})=\emptyset\), and therefore
  \(G\subseteq U_{\vec y,\mc U_n}\in\mc \tau(\mc U_n,n)\).
\end{proof}

\begin{theorem}\label{mengerFanTheorem}
  The following are equivalent for any \(T_{3\frac{1}{2}}\)
  topological space \(X\).
    \begin{itemize}
      \item \(X\) is \(\Omega M\)
            (resp. \(\Omega M^+\), \(\Omega M^{\plusMark}\)).
      \item \(C_p(X)\) is \(CFT\)
            (resp. \(CFT^+\), \(CFT^{\plusMark}\)).
      \item \(C_p(X)\) is \(CDFT\)
            (resp. \(CDFT^+\), \(CDFT^{\plusMark}\)).
    \end{itemize}
\end{theorem}

\begin{proof}
  Since \(\mc D_X\subseteq \Omega_{X,x}\), the second condition trivially
  implies the third. As \(C_p(X)\) is homogeneous, the \(C(D)FT\) properties
  follow from \(C(D)FT_{\vec 0}\). So the result follows from the
  previous lemmas.
\end{proof}

\section{A space which is \(CFT^+\) but not \(CDFT^{\plusMark}\)}

Our goal is to now demonstrate a space which is \(CFT^+\),
but not even \(CDFT^{\plusMark}\). To do so, we will find a space \(X\)
which is \(\Omega M^+\) but not \(\Omega M^{\plusMark}\), yielding \(C_p(X)\)
as our example.

@@

\begin{lemma}
  The following are equivalent for a regular topological space \(X\):
  \begin{itemize}
    \item \(X\) is \(\sigma\)-compact
    \item \(X\) is \(\Omega M^{\plusMark}\)
    \item \(X\) is \(M^{\plusMark}\)
  \end{itemize}
\end{lemma}

\begin{proof}
  The equivalence of \(\sigma\)-compact and \(M^{\plusMark}\) in regular spaces
  was shown in \cite{clontzMengerCMUC}. As \(\Omega M^{\plusMark}\)
  trivially implies \(M^{\plusMark}\), we need only demonstrate that
  if \(X=\bigcup_{n<\omega} K_n\) for \(K_n\) compact and increasing,
  then \(X\) is \(\Omega M^{\plusMark}\).

@@

\begin{theorem}\label{omega1OmegaMenger}
  Let \(\omega_1\) have the discrete topology. Then
  \(\onePtLind{\omega_1}\) is \(\Omega M^+\) but not \(\Omega M^{\plusMark}\).
\end{theorem}

\begin{proof}
  The proof that \(X=\onePtLind{\omega_1}\) is not
  \(\sigma\)-compact (and therefore not \(\Omega M^{\plusMark}\))
  follows from the fact that its countably infinite subsets
  are closed and discrete, so all of its compact subsets are finite.

@@

\begin{corollary}
  \(C_p(\onePtLind{\omega_1})\) is \(CFT^+\) but not \(CDFT^{\plusMark}\).
\end{corollary}

@@

\begin{question}
  Does there exist a separable subspace of \(C_p(\onePtLind{\omega_1})\)
  which is not \(CDFT^{\plusMark}\)?
\end{question}

@@

Barman and Dow
previously demonstrated that \(SS^+\) is equivalent to
\(SS^{\plusMark}\) amongst countable spaces.
A similar result by the author
showed that \(M^+\) is equivalent to \(M^{\plusMark}\) in second-countable
spaces. The following result generalizes both.

@@

  For \(t\in\omega^{<\omega}\), suppose
  \(Z_s\in\mc A\) has been defined for all \(s\leq t\). Note then that
  \(
    \{\sigma(\<Z_{t\rest1},Z_{t\rest2},\dots,Z_t,A\>):A\in\mc A\}
      \subseteq
    [\bigcup\mc A]^{<\omega}
  \)
  and therefore is countable.
  So choose \(Z_{t\concat\<n\>}\in\mc A\) for \(n<\omega\) such that
  \(
    \{\sigma(\<Z_{t\rest1},Z_{t\rest2},\dots,Z_t,A\>):A\in\mc A\}
      =
    \{\sigma(\<Z_{t\rest1},Z_{t\rest2},\dots,Z_t,Z_{t\concat\<n\>}\>):n<\omega\}
  \).

@@

  Define \(f\in\omega^\omega\) as follows.
  Let \(n<\omega\) and suppose that \(f\rest n\) has already
  been defined. Then choose \(f(n)<\omega\) such that
  \(
    \sigma(\<Z_{f\rest1},Z_{f\rest2},\dots,Z_{f\rest n},A_{b^{\leftarrow}(f\rest n)}\>)
      =
    \sigma(\<Z_{f\rest1},Z_{f\rest2},\dots,Z_{f\rest n},Z_{f\rest (n+1)}\>)
  \).

@@

\begin{corollary}[\cite{MR2868880}]
  A countable space is \(SS^+\) if and only if it is
  \(SS^{\plusMark}\).
\end{corollary}

@@

\begin{corollary}
  A second-countable space is \(\Omega M^+\) if and only if
  it is \(\Omega M^{\plusMark}\).
\end{corollary}

@@

\begin{corollary}[\cite{clontzMengerCMUC}]
  A second-countable space is \(M^+\) if and only if
  it is \(M^{\plusMark}\).
\end{corollary}

\begin{proof}
  An easy adaptation of the preceding proof, replacing \(\omega\)-covers
  with open covers, and replacing \(F\in[X]^{<\omega}\) with \(x\in X\).
\end{proof}

\section{Strong variants of selection principles and games}

Let \(\schStrongSelProp{\mc A}{\mc B},\schStrongSelGame{\mc A}{\mc B}\)
be the natural variants of
\(\schSelProp{\mc A}{\mc B},\schSelGame{\mc A}{\mc B}\) where each choice
by \(\plII\) must either be a single element or singleton
(whichever is more convenient for the proof at hand), rather than a finite
set. Convention calls for denoting these as
\term{strong} versions of the corresponding selection principles and games,
although the ``strong Menger'' property is commonly known as ``Rothberger''
who first investigated the principle in \cite{Rothberger1938}. We will thus
call ``strong \(\Omega\)-Menger'' ``\(\Omega\)-Rothberger'' and shorten it
with \(\Omega R\), and otherwise attach the prefix ``s''
when abbreviating to all other strong variants.

\begin{theorem}
  The following are equivalent for any topological space \(X\).
  \begin{itemize}
    \item \(X\) is \(sSS\) (resp. \(sSS^+\), \(sSS^{\plusMark}\)).
    \item \(X\) is separable and \(sCDFT\)
          (resp. \(sCDFT^+\), \(sCDFT^{\plusMark}\)).
    \item \(X\) has a countable dense subset \(D\) where
          \(sCDFT_x\) (resp. \(sCDFT_x^+\), \(sCDFT_x^{\plusMark}\))
          holds for all \(x\in D\).
  \end{itemize}
\end{theorem}

@@

  Let \(\sigma_i\) be a witness for \(sCDFT_{d_i}^{\plusMark}\)
  for each \(i<\omega\).
  Again, we will partition each
  attack by \(\plI\) according to \(p\) into \(\omega\)-many subattacks, and
  defeat each subattack to produce a blade of \(d_n\).

@@

  Let \(\alpha\in\mc D_X^\omega\), and let \(\alpha_i\) be its subsequence
  removing all terms of index \(n\) such that \(p(n)\not=i\).
  By \(sCDFT_{d_i}^{\plusMark}\), we have
  \[
    d_i
      \in
    \cl{\{\sigma_i(\alpha_i(n),n):n<\omega\}}
      =
    \cl{\{\tau(\alpha(n),n):n\in p^{\leftarrow}(i)\}}
      \subseteq
    \cl{\{\tau(\alpha(n),n):n<\omega\}}
  \]
  and as \(D\subseteq\cl{\{\tau(\alpha(n),n):n<\omega\}}\)
  it follows that
  \[
    X
      \subseteq
    \cl D
      \subseteq
    \cl{\cl{\{\tau(\alpha(n),n):n<\omega\}}}
      =
    \cl{\{\tau(\alpha(n),n):n<\omega\}}
  .\]
  Therefore \(\tau\) witnesses \(SS^{\plusMark}\).
\end{proof}
